---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vindecodr

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/burch-cm/vindecodr.svg?branch=master)](https://travis-ci.com/burch-cm/vindecodr)
<!-- badges: end -->

The goal of vindecodr is to provide an efficient programmatic interface to the 
US Department of Transportation (DOT) National Highway Transportation Safety 
Adminstration (NHTSA) vehicle identification number (VIN) decoder API, located at 
[https://vpic.nhtsa.dot.gov/api/](https://vpic.nhtsa.dot.gov/api/).

## Installation

You can install the released version of vindecodr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("vindecodr")
```

Or you can install the development version from [GitHub](https://github.com/burch-cm/vindecodr) with:

``` r
# install.packages("devtools")
devtools::install_github("burch-cm/vindecodr")
```

## Examples

### Find the Make and Model for a Given VIN:  

Managed fleet vehicle systems often need to confirm the information they have on 
file for a particular vehicle, such as the make, model, fuel type, etc. This can 
easily be accomplished by comparing the records on file with the manufacturer's 
values as encoded in the VIN.

```{r ex-1}
library(vindecodr)
given_vin <- "1C4BJWFGXDL531773"

vehicle_details <- decode_vin(given_vin)

knitr::kable(vehicle_details)
```

Single VINs are passed to the [Decode API Endpoing](https://vpic.nhtsa.dot.gov/api/vehicles/DecodeVINValues/).  
The same call can be used for up to 50 VINs. When multiple VINs are provided, 
the [Batch API Endpoint](https://vpic.nhtsa.dot.gov/api/vehicles/DecodeVINBatchValues/) is used instead. 
```{r ex-2}
library(vindecodr)

given_vins <- c("1C4BJWFGXDL531773",
                "JTHFF2C26B2515141",
                "WDBRF40J43F433102")

vehicle_details <- decode_vin(given_vins)
knitr::kable(vehicle_details[1:3])

```
See the [NHTSA API Documentation](https://vpic.nhtsa.dot.gov/api) for more detail on API endpoints.
